Cybersecurity Education and Accreditation:\\A UK Case Study

### 2019-06-22 FIE2019-final-TPJHD.tex
Restructured Intro and following section

Cybersecurity has increasingly been in the news over recent years, generally prompted by spectacular breaches, from credit reference agencies~\cite{equifax2017}, online dating websites~\cite{ashleymadison2015}, national airlines~\cite{BritishAirways2018a}, telecoms companies~\cite{talktalk2016}, and even between sovereign governments~\cite{ncsc2018}. These major breaches have had significant impact on both individual citizens and society in general, requiring attention across the spectrum for organisations of all sizes~\cite{Hannigan2019a}\footnote{Former Director of GCHQ: British equivalent of NSA.}:
\begin{quote}
``{\emph{...change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation.}}''
\end{quote}
\noindent
These global cybersecurity crises have compelled academic institutions to address the demand for educated cybersecurity professionals~\cite{McGettrick2013}. As no shared framework for ``cybersecurity'' as an academic discipline exists, growth has been unfocused and largely driven by training materials, which makes it harder to establish a common body of knowledge (for example, in the UK, \cite{Bristol2019a} is still a work in progress). An international perspective is harder still, as different nations use different criteria to define local needs~\cite{schneider2013}. As a result, new programmes entering this space are free to conceptualise, design, package and market their initiatives, as there is no globally accepted reference model for cybersecurity to allow employers or students to understand the extent or ambition of a given cybersecurity program~\cite{conklin-et-al:2014,Parrishetal2018a}.

% TC: check most recent versions of ACM curricula
% TC: check whether the ITiCSE report will be out this year?
With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as post-compulsory -- to respond to this situation, at the individual level and via recommended curricula~\cite{mcgettrick-et-al:sigcse2014,ACM2017b} and professional accreditation requirements~\cite{BCS2018a}. This is further reinforced by a wider focus on digital skills and computer science education reform, especially across the UK~\cite{brown-et-al:toce2014,murphy-et-al:programming2017,tryfonas+crick:petra2018}. There has been a recent ACM working group as part of the Innovation and Technology in Computer Science Education (ITiCSE) conference series~\cite{Parrishetal2018a}, but this has yet to report. The intention of this working group is to develop a taxonomy for approaches to cybersecurity education, resulting in improved standards and goals for many different types of cybersecurity programs; a further aim is to ``catalog existing [\dots] knowledge materials'', but there is no mention of any quality control over these.

@@

\subsection{Cybersecurity: for all or for specialists?}
%: \cite{JCNSS2018a} has only anecdotal evidence),

In one sense, this section title is a false dichotomy: there is a serious need for cybersecurity specialists (estimates vary, but are always large), but also all in IT need to know \emph{some} cybersecurity -- thus, there is a case for depth as well as breadth~\cite{manson+pike:2014}. This is not a new concern: see~\cite{Parr2014a} for concerns over five years ago, but it is a growing one. Recent evolution of cybersecurity shows that it has begun to take shape as a true academic perspective, as opposed to simply being a training domain for certain specialised jobs. More recent work presents cybersecurity as a ``meta-discipline''; that is, cybersecurity should be used as an aggregate label for a wide variety of similar disciplines, much in the same way that the terms ``engineering'' and ``computing'' are commonly used~\cite{Parrishetal2018b}.

%\subsection{Policy Context}

This need to build knowledge, skills and capacity in the area of cybersecurity has led to the establishment of a number of initiatives from a number of national governments, for example the UK's Cyber Security Strategy~\cite{UKCabinetOffice} (and the setting up of the UK National Cyber Security Centre), or National Initiative for Cybersecurity Education (NICE) in the USA \cite{NICE}.

The teaching of cybersecurity in higher education pre-dates these initiatives and there has been recognition of the need for the inclusion of cybersecurity as part of the Computer Science discipline for a number of years \cite{Hentea2006}. There has been a debate as to whether cybersecurity is distinct discipline from Computer Science \cite{McGettrick2013}. The consensus now is that cybersecurity is both a discipline in its own right and that cybersecurity should be taught within Computer Science and related degrees. There have been a number of international initiatives international to define curricula to support this for example the ACM Computer Science Curricula Recommendations \cite[which added ``Information Assurance and Security'' for the first time]{ACM2013a} and specialised cybersecurity Programmes \cite{ACMIEEEAISSIGSECIFIP}.

% TC to add policy+skills context
% inc. new EU cybersecurity Act: https://ec.europa.eu/commission/news/cybersecurity-act-2018-dec-11_en
% PPP e.g. Carr work and IEE Comp ref, Conklin paper
% Cyber Essentials Scheme

% should this be done at school?
There has been substantial computer science and digital skills curriculum reform across the UK~\cite{brown-et-al:toce2014,moller+crick:jce2018} --- but what has happened to the focus on cybersecurity? The Institute of Coding \cite{Davenportetal2019a}, designed to improve digital skills for UK graduates, does indeed mention cybersecurity, but merely as a sub-item in one work package (1.2a).

%This is basically note form: JHD suggests deleting
%UK national economic skills priority
%e.g. \url{https://www.gov.uk/government/publications/national-cyber-security-strategy-2016-to-2021}
%(esp. \url{https://publications.parliament.uk/pa/jt201719/jtselect/jtnatsec/706/70605.htm}
%(especially \cite{JCNSS2018a}
%and \url{https://www.ncsc.gov.uk/blog/skills-and-training} and
%\url{https://www.cybersecuritychallenge.org.uk/}).

%There is large-scale media attention on the ``cybersecurity skills gap''
%e.g. \url{https://www.contracts.mod.uk/do-features-and-articles/digital-skills-shortage-threatens-uk-cyber-security/}
%and
%\url{https://www.itpro.co.uk/cyber-security/31554/uk-government-lacks-urgency-in-tackling-cyber-security-skills-gap}
%etc -- link to UK Digital Strategy and UK Industrial Strategy.

% need a better title for this!
\subsection{Some Examples}

To illustrate some of these challenges, four examples are briefly explored: the European Union's General Data Protection Regulation (GDPR); Agile development; one industry sector (with rigorous demands for secure software); and impact of these cases upon one another.

On the one hand, GDPR (equally, the  California Consumer Privacy Act) has increased the corporate penalties for failure, and therefore the demand for various forms of cybersecurity specialists, both explicitly by requiring Data Protection Officers\footnote{\cite{EU292016a} places quite strong requirements on these: ``expertise in national and European data protection laws and practices and an in-depth understanding of the GDPR'', as well as ``principles of data processing'', ``data protection by design and by default'' and ``security of processing''. It is hard to envisage one professional possessing all these attributes and capabilities, and indeed ``DPO as a service'' is being promoted \cite{McCreanor2018d}.} and implicitly by causing organisations to re-think models for governance and assurance, and to invest more in cybersecurity. On the other hard, the growing publicity given to these, and the growing use of electronic payments, has also led to greater demand for expertise in this area.
% JHD what are these?  Also the next paragraph needs thinking about - TP - I added the next paragraph but now wonder if it should be deleted - I wonder if there is a point to be made about ''privacy by design and ''privacy by default'' but agile is covered better later.

%AI: GDPR essentially expects Cybersecurity to be in all coding. 
In particular, for the development of software that will operate within Europe and that processes personal data, the expectation of ``Privacy by Design'' and ``Privacy by Default'' have significant legal implications. However, ``Privacy by Design'' is no good without ``Security by Implementation'', and many security weaknesses are implementation weaknesses.
% can we evidence this?

A number of studies have documented the challenges of aligning security methods in Agile Practices \cite{vanderHeijden:2018:EPS:3239235.3267426,Bartsch2011a}. This further emphasises the need for mainstream software developers and by extension computer science graduates to be well-versed in relevant security practices.

This can be further illustrated by the demands of particular sectors for secure software. Considering the case of the Payments Industry \cite[6.6]{PCI2018b} which insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process, even after developers are trained annually in secure coding practices \cite[6.5]{PCI2018b}, cannot be trusted to deliver secure code.

\section{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The general public --- this is important, but there are many initiatives in this area (e.g. Cyber Essentials\footnote{Cyber Essentials is a UK Government-backed, industry-supported scheme to help organisations protect themselves against common online threats: \url{https://www.cyberessentials.ncsc.gov.uk}.}), which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general computer science graduate.
\item The generalist computer science masters graduate.
\item The specialist computer science graduate.
\item The specialist computer science masters graduate.
\end{enumerate}
The focus of this paper is on 2-3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science  students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?
\item[RQ3]Can accreditation by professional, statutory and regulatory bodies (PSRBs) enhance the provision of cybersecurity within a body's jurisdiction?
\end{description}

@@

In recent years the BCS has evolved its Accreditation Practices to promote and mandate the inclusion of cybersecurity within the programmes the body accredits. The timeline which this process has followed in Table \ref{table:1}.
%\begin{center}
  \begin{table}[h!]
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    IV. ACCREDITATION:RQ3 - A. Developing Expectations &   \\ \hline
    UK Government Cybersecurity Strategy \cite{UKCabinetOffice} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies - led by CPHC and (ISC)2 - leading to the development of Cybersecurity learning guidelines to be embedded into BCS accredited UK Computer Science and IT-related degree \cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium(ISC)2 \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    IV. ACCREDITATION:RQ3 - B. What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    IV. ACCREDITATION:RQ3 - C. Accreditation - what progress has been made? &  \\ \hline
    All visited HEIs expected to be fully compliant 
 (BCS follow a 5-year Accreditation Cycle)  & September 2020\\ \hline
  \end{tabular}
  \end{table}
%\end{center}

\subsection{Developing Expectations}
Internationally the expectations regarding both the breadth and depth of the expected cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many Governments, the UK Government has been actively been seeking ways to address this \cite{UKCabinetOffice}, \cite{UKCabinetOffice2014}. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees. This work initially lead to a white paper related to a proposal in the form of a white paper \cite{CPHCISC2014}, followed by a set of guidelines \cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on cybersecurity and the expectation that all computing graduates should have knowledge and skills in cybersecurity as they move towards Chartered status.

>>>>

Cybersecurity has increasingly been in the news over recent years, generally prompted by spectacular breaches, from credit reference agencies~\cite{equifax2017}, online dating websites~\cite{ashleymadison2015}, national airlines~\cite{BritishAirways2018a}, telecoms companies~\cite{talktalk2016}, and even between sovereign governments~\cite{ncsc2018}. These major breaches have had significant impact on both individual citizens and society in general, requiring attention across the spectrum for organisations of all sizes~\cite{Hannigan2019a}\footnote{Former Director of GCHQ: UK equivalent of NSA.}:
\begin{quote}
``{\emph{...[need to] change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation.}}''
\end{quote}
\noindent
These global cybersecurity crises have compelled academic institutions to address the demand for educated cybersecurity professionals~\cite{McGettrick2013}. As no shared framework for ``cybersecurity'' as an academic discipline exists, growth has been unfocused and largely driven by training materials, which makes it harder to establish a common body of knowledge (for example, in the UK, \cite{Bristol2019a} is still a work in progress). An international perspective is harder still, as different nations use different criteria to define local needs~\cite{schneider2013}. As a result, new programmes entering this space are free to conceptualise, design, package and market their initiatives, as there is no globally accepted reference model for cybersecurity to allow employers or students to understand the extent or ambition of a given cybersecurity program~\cite{conklin-et-al:2014,Parrishetal2018a}.

With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as post-compulsory -- to respond to this situation, at the individual level and via recommended curricula~\cite{mcgettrick-et-al:sigcse2014,ACM2017b} and professional accreditation requirements~\cite{BCS2018a}. This is further reinforced by a wider focus on digital skills and computer science education reform, especially across the UK~\cite{brown-et-al:toce2014,murphy-et-al:programming2017,tryfonas+crick:petra2018}. There has been a recent ACM working group as part of the Innovation and Technology in Computer Science Education (ITiCSE) conference series~\cite{Parrishetal2018a}, but this has yet to report its full findings. The intention of this working group is to develop a taxonomy for approaches to cybersecurity education, resulting in improved standards and goals for many different types of cybersecurity programmes; a further aim is to ``catalog existing [\dots] knowledge materials'', but there is no mention of any quality control over these.

@@

\section{Cybersecurity: for all or for specialists?}

In one sense, this title is a false dichotomy: there is a serious need for cybersecurity specialists (estimates vary, but are always large), but also all in IT need to know \emph{some} cybersecurity -- thus, there is a case for depth as well as breadth~\cite{manson+pike:2014}. This is not a new concern: see~\cite{Parr2014a} for concerns over five years ago, but it is a growing one.

This need to build knowledge, skills and capacity in the area of cybersecurity has also led to the establishment of a number of strategic policy initiatives from a number of national governments, for example the UK's Cyber Security Strategy~\cite{ukcyberstrategy:2016} (as well as the setting up of the UK National Cyber Security Centre, with increased scrutiny of what this means for the UK’s critical national infrastructure~\cite{lordscyberreport:2018}, as well as initiatives such as Cyber Essentials\footnote{Cyber Essentials is a UK Government-backed, industry-supported scheme to help organisations protect themselves against common online threats: \url{https://www.cyberessentials.ncsc.gov.uk}.}), the EU Cybersecurity Act~\cite{eucyber2018} (which reinforces the mandate of the EU Agency for Cybersecurity -- ENISA -- the European Union Agency for Network and Information and Security), or the National Initiative for Cybersecurity Education (NICE) in the USA~\cite{NICE}.

The teaching of cybersecurity in higher education pre-dates these initiatives and there has been recognition of the need for the inclusion of cybersecurity as part of the computer science discipline for a number of years~\cite{Hentea2006,schneider2013}. There have been a number of international initiatives international to define curricula to support this, for example the ACM Computer Science Curricula Recommendations~\cite[which added ``Information Assurance and Security'' for the first time]{ACM2013a} and specialised cybersecurity Programmes \cite{ACMIEEEAISSIGSECIFIP}. There has been a debate as to whether cybersecurity is distinct discipline from Computer Science \cite{McGettrick2013}. The consensus increasingly is that cybersecurity is both a discipline in its own right and that cybersecurity should be taught within Computer Science and related degrees. Recent evolution of cybersecurity shows that it has begun to take shape as a true academic perspective, as opposed to simply being a training domain for certain specialised jobs. More recent work presents cybersecurity as a ``meta-discipline''; that is, cybersecurity should be used as an aggregate label for a wide variety of similar disciplines, much in the same way that the terms ``engineering'' and ``computing'' are commonly used~\cite{Parrishetal2018b}.

Further to the substantial computer science and digital skills curriculum reform across the UK~\cite{brown-et-al:toce2014,tryfonas+crick:petra2018}, should cybersecurity be formally taught in schools, as part of a compulsory education? While aspects of ``e-safety'' and principles of protecting personal data are clearly visible in formal curricula~\cite{moller+crick:jce2018}, the majority of UK schoolchildren's exposure to cybersecurity skills is through national competitions, for example Cyber Security Challenge UK\footnote{\url{https://www.cybersecuritychallenge.org.uk}}. The Institute of Coding~\cite{Davenportetal2019a}, a \pounds40m+ initiative by the UK Government to transform the digital skills profile of the country, primarily focused on university graduates, does indeed mention cybersecurity, but merely as a sub-item in one work package (1.2a).

% have merged into previous section
%UK national economic skills priority
%e.g. \url{https://www.gov.uk/government/publications/national-cyber-security-strategy-2016-to-2021}
%(esp. \url{https://publications.parliament.uk/pa/jt201719/jtselect/jtnatsec/706/70605.htm}
%(especially \cite{JCNSS2018a}
%and \url{https://www.ncsc.gov.uk/blog/skills-and-training} and
%\url{https://www.cybersecuritychallenge.org.uk/}). 
%There is large-scale media attention on the ``cybersecurity skills gap''
%e.g. \url{https://www.contracts.mod.uk/do-features-and-articles/digital-skills-shortage-threatens-uk-cyber-security/}
%and
%\url{https://www.itpro.co.uk/cyber-security/31554/uk-government-lacks-urgency-in-tackling-cyber-security-skills-gap}
%etc -- link to UK Digital Strategy and UK Industrial Strategy.

% need a better title for this!
% \subsection{Some Examples}

% To illustrate some of these challenges, four examples are briefly explored: the European Union's General Data Protection Regulation (GDPR); Agile development; one industry sector (with rigorous demands for secure software); and impact of these cases upon one another.

% On the one hand, GDPR (equally, the  California Consumer Privacy Act) has increased the corporate penalties for failure, and therefore the demand for various forms of cybersecurity specialists, both explicitly by requiring Data Protection Officers\footnote{\cite{EU292016a} places quite strong requirements on these: ``expertise in national and European data protection laws and practices and an in-depth understanding of the GDPR'', as well as ``principles of data processing'', ``data protection by design and by default'' and ``security of processing''. It is hard to envisage one professional possessing all these attributes and capabilities, and indeed ``DPO as a service'' is being promoted \cite{McCreanor2018d}.} and implicitly by causing organisations to re-think models for governance and assurance, and to invest more in cybersecurity. On the other hard, the growing publicity given to these, and the growing use of electronic payments, has also led to greater demand for expertise in this area.
% % JHD what are these?  Also the next paragraph needs thinking about - TP - I added the next paragraph but now wonder if it should be deleted - I wonder if there is a point to be made about ''privacy by design and ''privacy by default'' but agile is covered better later.

% %AI: GDPR essentially expects Cybersecurity to be in all coding. 
% In particular, for the development of software that will operate within Europe and that processes personal data, the expectation of ``Privacy by Design'' and ``Privacy by Default'' have significant legal implications. However, ``Privacy by Design'' is no good without ``Security by Implementation'', and many security weaknesses are implementation weaknesses.
% % can we evidence this?

% A number of studies have documented the challenges of aligning security methods in Agile Practices \cite{vanderHeijden:2018:EPS:3239235.3267426,Bartsch2011a}. This further emphasises the need for mainstream software developers and by extension computer science graduates to be well-versed in relevant security practices.

% This can be further illustrated by the demands of particular sectors for secure software. Considering the case of the Payments Industry \cite[6.6]{PCI2018b} which insists on either independent code reviews by security specialists or a Web Application Firewall: essentially saying that the normal development process, even after developers are trained annually in secure coding practices \cite[6.5]{PCI2018b}, cannot be trusted to deliver secure code.

\section{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The general public --- this is important, but there are many initiatives in this area, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general computer science graduate.
\item The generalist computer science masters graduate.
\item The specialist computer science graduate.
\item The specialist computer science masters graduate.
\end{enumerate}
The focus of this paper is on 2-3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science  students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?
\item[RQ3]Can accreditation by professional, statutory and regulatory bodies (PSRBs) enhance the provision of cybersecurity within a body's jurisdiction?
\end{description}

@@

In recent years the BCS has evolved its Accreditation Practices to promote and mandate the inclusion of cybersecurity within the programmes the body accredits. The timeline which this process has followed in Table \ref{table:1}.
%\begin{center}
  \begin{table}[h!]
  \caption{Timeline of the development of Cybersecurity expectations}
  \label{table:1}
  \begin{tabular}{ | p{6cm} |p{1.5cm} |}
    \hline
    IV. ACCREDITATION:RQ3 - A. Developing Expectations &   \\ \hline
    UK Government Cybersecurity Strategy \cite{ukcyberstrategy:2016} & November 2011 \\ \hline
    Three workshops of a consortium of industry, academia and government bodies - led by CPHC and (ISC)2 - leading to the development of Cybersecurity learning guidelines to be embedded into BCS accredited UK Computer Science and IT-related degree \cite{CPHCISC2}  & 2013 to June 2015 \\ \hline
    UK Government report Cybersecurity Skills, Business Perspectives and Government's Next Steps Report Released \cite{UKCabinetOffice2014} & March 2014  \\ \hline
    Council of Professors and Heads of Computing (CPHC) Identifies Cybersecurity as one the top 3 concerns in Computing & April 2014 \\ \hline
    Joint Development of White Paper from CPHC and The International Information Systems Security Certification Consortium(ISC)2 \cite{CPHCISC2014} & April -November 2014 \\ \hline
    Extended Cybersecurity Criteria included in BCS Accreditation Guidelines \cite{BCS2018a}& June 2015 \\
    \hline
    IV. ACCREDITATION:RQ3 - B. What does the BCS tell Universities? & \\ \hline
    Cybersecurity Principles Roadshow & March-April 2016 \\ \hline
    IV. ACCREDITATION:RQ3 - C. Accreditation - what progress has been made? &  \\ \hline
    All visited HEIs expected to be fully compliant 
 (BCS follow a 5-year Accreditation Cycle)  & September 2020\\ \hline
  \end{tabular}
  \end{table}
%\end{center}

\subsection{Developing Expectations}
Internationally the expectations regarding both the breadth and depth of the expected cybersecurity coverage has been the subject of much discussion, debate and analysis. Like many Governments, the UK Government has been actively been seeking ways to address this \cite{ukcyberstrategy:2016}, \cite{UKCabinetOffice2014}. In parallel to the work complete by the ACM \cite{ACM2013a}, in the UK considerable effort was taken to ensure Industry, Higher Education, Government and the related Professional Bodies collaborated on a set of guidelines which are to the benefit of the various stakeholders and wider society \cite{Irons2016}. In 2013, an initiative was set up by (ISC)2, CPHC (the representative body of Computer Science Departments) and the Cabinet Office to examine embedding cybersecurity into undergraduate degrees in the UK. Three workshops in 2013 and 2015 attempted to define the principles of cybersecurity education and proposed a framework for embedding these principles in UK Computing Science curricula. Attendees at the workshops included industry, professional bodies, UK government departments and more than 30 Universities that offer undergraduate Computing Science degrees. This work initially lead to a white paper related to a proposal in the form of a white paper \cite{CPHCISC2014}, followed by a set of guidelines \cite{CPHCISC2}. The BCS agreed to adopt the outputs into their accreditation criteria. This was the first time that cybersecurity has been extensively referenced within accreditation criteria for computing and IT-related degrees. The fact that cybersecurity is included as a  component of the BCS accreditation criteria, reflects the importance placed on cybersecurity and the expectation that all computing graduates should have knowledge and skills in cybersecurity as they move towards Chartered status.
